---
title: "*easylca* data diagnosis report for `r params$title`"
date: "*created `r format(Sys.time(), '%H:%M, %B %d, %Y')`*"
output: 
  html_document:
    css: diagnosis_report_template.css
params:
  data: NULL
  idcol: NULL
  title: NULL
---

## Variable Types

```{r types, echo=F}
data <- params$data
idcol <- params$idcol
title <- params$title
types <- sapply(dplyr::select(data, -all_of(idcol)), class)
discrete <- types[types == 'integer'] %>% names()
continuous <- types[types == 'numeric'] %>% names()
is_discrete <- length(discrete) > 0
is_continuous <- length(continuous) > 0
is_correlations <- length(continuous) > 1
```

**N = `r nrow(data)`** observations, id variable is *`r idcol`*.\

**`r length(continuous)` continuous indicators** (type `numeric`):\
*`r continuous`*

**`r length(discrete)` discrete indicators** (type `integer > 1`, max 10 levels):\
*`r discrete`*

## Missings

```{r missings_calc, echo=F}
missings <- sapply(data %>% dplyr::select(-dplyr::all_of(idcol)),
       function(x) 1 - length(na.omit(x)) / length(x))
missings <- data.frame(var = names(missings), 
                       relfreq_na = missings) %>% 
  dplyr::arrange(dplyr::desc(relfreq_na)) %>% 
  dplyr::filter(relfreq_na != 0) %>% 
  dplyr::mutate(label = sprintf('%.0f%%', relfreq_na * 100))
is_missings <- nrow(missings) > 0
```

```{r missings_plot, echo=F, fig.height=nrow(missings)*0.4+0.75, warning=F}
if(is_missings){
  ggplot2::ggplot(missings, ggplot2::aes(y = forcats::fct_rev(forcats::fct_inorder(var)), x = relfreq_na)) + 
    ggplot2::geom_col(ggplot2::aes(fill = relfreq_na), show.legend = F) + 
    ggplot2::scale_x_continuous(expand = ggplot2::expansion(mult = c(0, 0.025)),
                                limits = c(0,1), position = 'top')+ 
    ggplot2::scale_fill_gradientn(colors = c("grey85", "#c40d20"),
                                  values = scales::rescale(c(0, 0.4))) + 
    ggplot2::xlab('relative frequency of NAs') + 
    ggplot2::ylab('')+
    ggplot2::geom_text(ggplot2::aes(label = label), hjust = 0, nudge_x = 0.01) + 
    ggplot2::theme_minimal() + 
    ggplot2::theme(legend.position = 'none', 
          panel.grid = ggplot2::element_blank(), 
          axis.title.x = ggplot2::element_text(color = 'grey45', size = 14, hjust = 0),
          axis.text.x = ggplot2::element_blank(), 
          axis.text.y = ggplot2::element_text(size = 14, face = 'italic'))
}
```

```{r missings_no_indicators, echo=F, results='asis'}
if(! is_missings){cat('There are no missing values.')}
```

All other indicators do not have missing values.

## Spearman correlations between continuous indicators

```{r correlations, echo=F, fig.height=length(continuous)*0.5+1.5, fig.width=length(continuous)*0.5+2, warning=F}
if(is_correlations){
  cor_matrix <- stats::cor(data %>% 
                             dplyr::select(all_of(continuous)),
                           use = 'pairwise.complete.obs',
                           method = "spearman")
  cor_df <- as.data.frame(cor_matrix)
  cor_long <- cor_df %>%
    tibble::rownames_to_column(var = "Var1") %>%
    tidyr::pivot_longer(cols = -Var1, names_to = "Var2", values_to = "value") %>% 
    dplyr::mutate(lower_triangular = match(Var1, unique(Var1)) > match(Var2, unique(Var2)), 
                  label = sprintf('%.2f', value), 
      Var1 = forcats::fct_inorder(Var1), 
      Var2 = forcats::fct_inorder(Var2))
  
  ggplot2::ggplot(cor_long, ggplot2::aes(Var1, Var2, 
                                         fill = ifelse(lower_triangular,
                                                       NA, value))) +
    ggplot2::geom_tile(color = "white") +
    ggplot2::scale_x_discrete(position = 'top') +
    ggplot2::scale_fill_gradient(low = "white", high = "#c40d20",na.value = "white") +
    ggplot2::geom_text(ggplot2::aes(label = ifelse(lower_triangular, '', label)),
                       color = 'grey25')+
    ggplot2::theme_minimal() +
    ggplot2::labs(x = "", y = "") +
    ggplot2::theme(axis.text.x = ggplot2::element_text(size = 14, 
                                                       angle = 45, hjust = 0), 
                   axis.text.y = ggplot2::element_text(size = 14), 
                   legend.position = 'none')
} 
```

```{r correlations_no_indicators, echo=F, results='asis'}
if(!is_correlations){
  cat('There are less than 2 continuous indicators. Thus, no Spearman correlations are computed.')
}
```

## Indicator distributions

#### [Continuous indicators]{style="color: #c40d20"}

```{r continuous_histograms, echo=F, fig.height=length(continuous)*1.25+0.001,  warning=F}
if(length(continuous)>1){
  continuous_data <- data %>% dplyr::select(dplyr::all_of(continuous)) %>% 
    tidyr::pivot_longer(cols = everything(),
                        names_to = "variable", values_to = "value")
  
  n_bins <- 80
  ggplot2::ggplot(continuous_data, 
                  ggplot2::aes(x = value)) + 
    ggplot2::geom_histogram(fill = 'grey45', bins = n_bins, na.rm = T) + 
    ggplot2::facet_wrap(~ variable, ncol = 2, scales = 'free')+ 
    ggplot2::theme_minimal() + 
    ggplot2::ylab('frequency') +
    ggplot2:::theme(strip.text = ggplot2::element_text(size = 14, face = 'bold', 
                                              hjust = 0), 
                    axis.title = ggplot2::element_text(color = 'grey45'),
                    axis.text = element_text(color = 'grey45'), 
                    panel.grid = element_blank())
}
```

```{r continuous_histograms_no_indicators, echo=F, results='asis'}
if(! is_continuous){cat('There are no continuous indicators.')}
```

#### [Robust distribution parameters of continuous indicators]{style="color: #c40d20"}

```{r continuous_distribution_parameters, echo=F, fig.width=4, fig.height=4,warning=F}
if(length(continuous)>1){
  medians <- continuous_data %>% dplyr::group_by(variable) %>% 
    dplyr::summarize(median = median(value, na.rm = T))
  IQR <- continuous_data %>% dplyr::group_by(variable) %>% 
    dplyr::summarize(iqr = IQR(value, na.rm = T) * 1.5) # equals variance for Gaussian
  parameters <- suppressMessages(dplyr::inner_join(medians, IQR))
  x_max <- max(parameters$iqr)
  y_max <- max(parameters$median)
  
  ggplot2::ggplot(parameters, ggplot2::aes(x = iqr, y = median)) + 
    ggplot2::geom_point() + 
    ggplot2::scale_x_continuous(expand = ggplot2::expansion(mult = c(0.05, 
                                                                     0.3)))+
    ggplot2::geom_text(ggplot2::aes(label = variable), 
                       hjust = 0, 
                       nudge_x = 0.01 * x_max, 
                       nudge_y = 0.01 * y_max) + 
    ggplot2::labs(x = 'Interquartile range x 1.5', y = 'Median') + 
    ggplot2::theme_minimal() + 
    ggplot2::theme(axis.text = element_text(color = 'grey45'))
}
```

```{r continuous_distribution_parameters_no_indicators, echo=F, results='asis'}
if(! is_continuous){cat('There are no continuous indicators.')}
```

#### [Discrete indicators]{style="color: #c40d20"}

```{r discrete_histograms, echo=F, fig.height=length(discrete)*1+0.001,  warning=F}
if(length(discrete)>1){
  discrete_data <- data %>% dplyr::select(dplyr::all_of(discrete)) %>% 
    tidyr::pivot_longer(cols = everything(),
                        names_to = "variable", values_to = "value")
  ggplot2::ggplot(discrete_data, 
                  ggplot2::aes(y = as.factor(value))) + 
    ggplot2::geom_bar(fill = 'grey45', stat = 'count',
                            na.rm = T) + 
    ggplot2::labs(x = 'frequency', y = '') + 
    ggplot2::facet_wrap(~ variable, ncol = 3, scales = 'free_y')+ 
    ggplot2::theme_minimal() + 
    ggplot2:::theme(strip.text = ggplot2::element_text(size = 12, face = 'bold', 
                                              hjust = 0), 
                    axis.title = ggplot2::element_text(color = 'grey45'),
                    axis.text.y = element_text(size =  12, color = 'black'), 
                    axis.text.x = element_text(color = 'grey45'), 
                    panel.grid = element_blank())
} 
```

```{r discrete_histograms_no_indicators, echo=F, results='asis'}
if(!is_discrete){cat('There are no discrete indicators.')}
```
